Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-07-09 aggregation/agg-multioutput.tex
backport post-accept changes

The treatment of multi-functional activities in LCA is a topic of constant discussion among practitioners and theorists.  While the question of the correct, appropriate, or ideal method of apportioning impacts among co-products cannot be resolved in general, the utility of a disclosure framework must be to \textit{express} transparently how co-production was resolved within a given foreground model.  Majeau-Bettez et al. (2014) recently provided a general framework (referred to hereafter as MWS14) for describing the treatment of co-products, and I adopt that framework here to show how the technique used to handle co-production can be disclosed transparently for foreground processes.

>>>>

The treatment of multi-functional activities in LCA is a topic of constant discussion among practitioners and theorists.  While the question of the correct, appropriate, or ideal method of apportioning impacts among co-products cannot be resolved in general, the utility of a disclosure framework must be to \textit{express} transparently how co-production was resolved within a given foreground model.  Majeau-Bettez et al. (\citeyear{Majeau_Bettez_2014}) recently provided a general framework (referred to hereafter as MWS14) for describing the treatment of co-products, and I adopt that framework here to show how the technique used to handle co-production can be disclosed transparently for foreground processes.

### 2018-07-09 aggregation/equivalence.tex
backport post-accept changes

There is a level of confusion about the differing implications of process-based LCA inventory analysis as described in Heijungs and Suh (2002), and input-output analysis using a Leontief matrix.  In fact, these two techniques were shown to be equivalent in Suh et al, 2010\footnote{\doi{10.1111/j.1530-9290.2010.00235.x}; see full text for citation.}, whose abstract declares: ``the article shows that the partitioning method in LCA is equivalent to the industry-technology model in input-output economics, and system expansion in LCA is equivalent to the by-product-technology model in input-output output economics.''  The article does indeed show convincingly that ``the two data types can be hybridized without the loss of methodological consistency'' (p.345).

>>>>

There is a level of confusion about the differing implications of process-based LCA inventory analysis as described in Heijungs and Suh (\citeyear{Heijungs2002}), and input-output analysis using a Leontief matrix.  In fact, these two techniques were shown to be equivalent in Suh et al, (\citeyear{Suh_JIE_2010}), whose abstract declares: ``the article shows that the partitioning method in LCA is equivalent to the industry-technology model in input-output economics, and system expansion in LCA is equivalent to the by-product-technology model in input-output output economics.''  The article does indeed show convincingly that ``the two data types can be hybridized without the loss of methodological consistency'' (p.345).
